The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
social scale edits

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF? / see EVW comment-->. Specifically, we
modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group.

>>>>

We modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group. We assumed these scales represented visual (short distance) to auditory (long distance) sensory modalities of caribou.
